---
title: Code to analyze tree structure from an image
author: Kwanghun Choi
output: pdf_document
---
# Install and load essential packages for analysis
```{r}
pacman::p_load("imager", "tidyverse", "foreach", "segmented", "rmarkdown", "pander")
```

# Assign folders for analysis
```{r}
data_path <- c("~/Kwanghun/Tasks/DeepLearning/lelab/Data/SemanticSegmentation/")
data_name <- c("GSV_360_20200924")
```

# Load data
```{r}
# Image With Yolo annotation pictures
Yolo <- load.image(paste0(data_path, data_name, "/raw/Y_ZE.jpg")) 
# Image withOut (Ohne) Background pictures
SS <- load.image(paste0(data_path, data_name, "/result0/semantic/semantic_pred_0.png"))  
```

# Plot and check cropping regions
```{r}
# Show two pictures in a row
par(mfrow=c(1,2))
# 1. Image With Background
plot(Yolo)
# Create boundary for a tree manually
abline(v=100, col="red") ; abline(v=300, col="red") ; abline(244,0, col="red"); abline(244,0, col="red")
T1 <- c(100, 300, 244, 832)
abline(v=535, col="red") ; abline(v=715, col="red") ; abline(275,0, col="red"); abline(244,0, col="red")
T2 <- c(535, 715, 275, 832)
abline(v=650, col="red") ; abline(v=765, col="red") ; abline(302,0, col="red"); abline(244,0, col="red")
T3 <- c(650, 765, 302, 832)
abline(v=836, col="red") ; abline(v=975, col="red") ; abline(294,0, col="red"); abline(244,0, col="red")
T4 <- c(836, 975, 294, 832)
abline(v=873, col="red") ; abline(v=1143, col="red"); abline(148,0, col="red")  ; abline(244,0, col="red")
T5 <- c(873, 1143, 8, 832)
abline(v=1075, col="red"); abline(v=1585, col="red"); abline(150,0, col="red"); abline(244,0, col="red")
T6 <- c(1075, 1585, 150, 832)
abline(v=1460, col="red"); abline(v=1664, col="red"); abline(208,0, col="red" ; abline(244,0, col="red"))
T7 <- c(1460, 1664, 208, 832)

abline(416, 0,col="red")

# 2. Image withOut Background
plot(SS)
```

# Information of pictures
```{r}
W <- nrow(Yolo) # Width of the picture
H <- ncol(Yolo) # Height of the picture
VP <- H/2       # View point of the picture
VH <- 2.0         # Height of the Camera
```


# Split images
```{r}
# Split image with imsub
Spliter <- function(Img, BBox){ Img %>% imsub(x >= BBox[1] & x <= BBox[2]) %>% imsub(y >= BBox[3] & y <= BBox[4]) }
SS_1 <- Spliter(SS, BBox = c(100,300,1, H))
```


# Image analysis


```{r}
# Remove all other colors except those of vegetation pixels from the semented image
# Image extractor
TreeExtractor <- 
    function(Img){
        IO <- Img
        R(IO)[which(!R(IO)[] * 255 == 107)] <- NA
        G(IO)[which(!G(IO)[] * 255 == 142)] <- NA
        B(IO)[which(!B(IO)[] * 255 == 35)] <- NA
        return(IO)
    }

# Check the result map
TreeOnly <- TreeExtractor(SS_1)
plot(TreeOnly)
```

# Calculate pixel width of the individual tree
```{r}
# Extract the range of tree height 
TreeOnly_col <- as.numeric(colSums(R(TreeOnly), na.rm=T)) %>% ifelse(. < 1, NA, .)
TreeOnly_min <- ((TreeOnly_col * 0 + 1) * c(1:H)) %>% min(.,na.rm=T)
TreeOnly_max <- ((TreeOnly_col * 0 + 1) * c(1:H)) %>% max(.,na.rm=T)
# Calculate the pixel width of the tree
PW <- VH/(TreeOnly_max - VP)
```

# Cut verical frame fit to the tree size
```{r}
TreeFit <- Spliter(TreeOnly, c(1, nrow(TreeOnly), TreeOnly_min, TreeOnly_max))
plot(TreeFit)
```

## 2. count values from bottom to top
```{r}
# In this part, I calculated the vegetation pixel by each row
out <- foreach(i = seq(ncol(TreeFit),1, -1), .combine=c) %do% {
    length(which(!is.na(R(TreeFit)[,i]+G(TreeFit)[,i]+B(TreeFit)[,i])))
}

# Remove the row with zero vegetation pixels
out.nonzero <- out[out[]>0]
out.df <- data.frame(PixW = out.nonzero) %>%
            mutate(PixH = c(1:nrow(.))) 
plot(PixW ~ PixH, data=out.df)

# Check the first change point of the plot
out.cp <- strucchange::Fstats(PixW ~ 1, data=out.df)
abline(v=out.cp$breakpoint, col="red")
```

## 3. Create Tree inventory table
```{r}
# Create Tree inventory in pixels
Tree_W   <- max( out.df$PixW, na.rm=T)            # Crown width
Tree_H   <- nrow(out.df)                          # Tree Height
Tree_BH  <- out.cp$breakpoint                     # Height below crown.
Tree_DBH <- quantile(out.df$PixW[1:Tree_BH], 0.1) # DBH which is assumed to be a median width below crown.

# Create Table for the metric.
M <- data.frame(Tree_H, Tree_W, Tree_BH, Tree_DBH)

# Convert Pixels to real units
#FocLmm <- 3.94                              # Focal length of Pocophone F1
#PixSizeCCD <- 1.4 * 10^-6                      # Pixel width of the camera ccd of Pocophone F1
#Dist <- 100                                  # Distance from the camera to the object

# Calculate width of a pixel in the image
#PixSizeIMG <- Dist * PixSizeCCD / FocLmm
PixSizeIMG <- 0.025 # Assumption of PixSizeIMG of GSV
# Final table
pander(M *  PW)
```

## Supl. Extract colors of vegetation (107, 142, 35) from panoptic-deeplab hompasge (https://github.com/bowenc0221/panoptic-deeplab/issues/42)

0  : "road"
1  : "sidewalk"
2  : "building"
3  : "wall"
4  : "fence"
5  : "pole" (153, 153, 153) 
6  : "traffic light"
7  : "traffic sign"
8  : "vegetation" (107, 142, 35)
9  : "terrain"
10 : "sky"
11 : "person"
12 : "rider"
13 : "car"
14 : "truck"
15 : "bus" (0, 60, 100)
16 : "train"
17 : "motorcycle"
18 : "bicycle"

